### 2017-08-09 R/NHTS.Rmd
Removed TravelSurvey step
No longer dependent on the package TravelSurvey

# U.S. National Household Travel Surevy

@@

NHTS.person <- with(PERV2PUB,{
                    data.frame(HOUSEID = HOUSEID,
                               PERSONID = PERSONID,
                               SEX = as.factor(ifelse(R_SEX=="1", "M", ifelse(R_SEX=="2", "F", NA))),
                               AGE = as.factor(ITHIM:::convertToAgeClass(R_AGE)),
                               MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                               HHSTATE = as.character(HHSTATE),
                               # HHS = as.character(convertToHHS(as.character(HHSTATE))),
                               MSA_ID = as.character(as.integer(HHC_MSA)), stringsAsFactors = FALSE)
})

@@

person.df <- with(NHTS.person,{
    data.frame(houseID=HOUSEID, subjectID=PERSONID, sex = SEX, age = AGE, location = MSA_ID)
    })

@@

NHTS.TravelSurvey <- new("TravelSurvey", person = person.df, trip = trip.df)

saveRDS(NHTS.TravelSurvey, file = "~/GHI/R/data/NHTS.TravelSurvey.rds")
```

```{r TravelSurvey, eval = TRUE, fig.width = fig.width, echo = FALSE}
NHTS.ts <- readRDS(file = "~/GHI/R/data/NHTS.TravelSurvey.rds")
NHTS.df <- dplyr::left_join(NHTS.ts@person, NHTS.ts@trip, by = c("houseID","subjectID"))
NHTS.df <- within(NHTS.df, {
    id <- paste0(houseID,"-",subjectID)
    duration <- ifelse(is.na(duration), 0, duration)
    mode <- factor(mode, levels = c("walk","cycle","other"))
    location <- location
})
saveRDS(NHTS.df, file = "~/GHI/R/data/NHTS.df.rds")
```

>>>>

 U.S. National Household Travel Surevy

@@

NHTS.person <- with(PERV2PUB,{
                    data.frame(HOUSEID = HOUSEID,
                               PERSONID = PERSONID,
                               SEX = as.factor(ifelse(R_SEX=="1", "M", ifelse(R_SEX=="2", "F", NA))),
                               AGE = as.factor(ITHIM:::convertToAgeClass(R_AGE)),
                               MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                               HHSTATE = as.character(HHSTATE),
                               # HHS = as.character(convertToHHS(as.character(HHSTATE))),
                               MSA_ID = as.character(as.integer(HHC_MSA)), stringsAsFactors = FALSE,
                               HHFAMINC = as.factor(HHFAMINC))
})

@@

person.df <- with(NHTS.person,{
    data.frame(houseID=HOUSEID, subjectID=PERSONID, sex = SEX, age = AGE, location = MSA_ID, income = HHFAMINC)
    })

@@

#NHTS.TravelSurvey <- new("TravelSurvey", person = person.df, trip = trip.df)

#saveRDS(NHTS.TravelSurvey, file = "~/GHI/R/data/NHTS.TravelSurvey.rds")
```

```{r TravelSurvey2, eval = TRUE, fig.width = fig.width, echo = FALSE}
#NHTS.ts <- readRDS(file = "~/GHI/R/data/NHTS.TravelSurvey.rds")

#NHTS.df <- dplyr::left_join(NHTS.ts@person, NHTS.ts@trip, by = c("houseID","subjectID"))

NHTS.df <- dplyr::left_join(person.df, trip.df, by = c("houseID","subjectID"))
NHTS.df <- within(NHTS.df, {
    id <- paste0(houseID,"-",subjectID)
    duration <- ifelse(is.na(duration), 0, duration)
    mode <- factor(mode, levels = c("walk","cycle","other"))
    location <- location
})
saveRDS(NHTS.df, file = "~/GHI/R/data/NHTS.df.rds")
```
